% Move 1 - Background/introduction/situation 
Ships with wind-assisted propulsion systems (WAPS) are often equipped with large rudders to compensate for WAPS-induced drifting forces. The WAPS also significantly affects the effectiveness of mathematical models used to describe the ship's manoeuvring characteristics. In this study, a modular manoeuvring model is proposed to enhance the original MMG model, aiming to produce accurate manoeuvring simulations for ships with WAPS.

% Move 3 - Methods/materials/subjects/procedures 
Methods of virtual captive tests (VCT) are proposed to recreate the forces acting on WAPS ships during free-running model tests (FRMT) in motor mode, identifying all the parameters in the modular model. The hydrodynamic damping coefficients within the model are determined through linear regression of the VCT data. The added masses are then determined from pure yaw and pure sway simulations using a fully nonlinear potential flow (FNPF) panel method.

% Move 4 - Results/findings 
Two ships designed for WAPS, wPCC and Optiwise, are used to validate the proposed method based on the inverse dynamics of their experimental model tests. The wPCC is equipped with a semi-empirical rudder that has previously shown to work well for this twin-rudder ship. The Optiwise single rudder is modeled with a new quadratic version of the MMG rudder model, proposed in this paper. It is concluded that inverse dynamics analysis, together with state VCTs, is an efficient way to analyze the models, and the manoeuvring model can be efficiently identified when correct VCTs are used in the proposed method. However, the inverse dynamics analysis also revealed potential errors in the wPCC VCT data due to false assumptions about wave generation and roll motion. The Optiwise test case, where these assumptions should be more valid, showed much better agreement with the FRMT inverse dynamics.

% Move 5 - Discussion/conclusion/significance
%This paper has proposed a new version of the MMG model that produced accurate simulations when identified on correct VCT data. .

%    

%For the wPCC ship with double rudders, large discrepancies were observed between the closed loop manoeuvring predictions by the identified model and tests, due to the incapability of VCTs to model rudder forces, and asymmetric patterns of flows on the two rudders. When the measurement of rudder forces is available for the Optiwise ship, the MMG model identified by the proposed method can perfectly predict the ship’s manoeuvring motions compared to the tests.
