Ships over 100 meters must fulfill requirements on maneuverability to ensure navigation safety \citep{imoStandardsShipManoeuvrability2002}. As the urgent demands to decarbonize shipping industry, wind-assisted propulsion (WAP) systems might become one of essential equipment onboard future ships (CE Delft 2016). Ships with WAPS should be equipped with large rudders to compensate large side forces to comply with the maneuverability requirements (WASP 2023). Ship maneuvering characteristics can be predicted by various approaches, such as model tests (ITTC 2008), numerical simulations by computational fluid dynamics (CFD) (el Moctar et al. 2016, Duman and Bal 2022), and mathematical modelling (Abkowitz 1980, Fossen 2011, Yasukawa and Yoshimura 2015,  Alexandersson et al. 2024, etc.). The model tests are often recognized as the most reliable way to predict a ship’s maneuverability, the captive model tests or planar motion mechanism model tests (ITTC 2008), and free running model tests (ITTC2021). They often served as references for other prediction methods, for example for the validation in several benchmark study of different CFD simulations such as by Stern et al. (2011), Sakamoto et al. (2012), Yoon et al. (2015), Yasukawa et al. (2021), etc., and used for system identification of mathematical maneuvering modeling and verifications, such as by Luo et al. (2016), Xu et al.(2019), Wang et al. (2020), Axelandersson et al. (2022).Due to flexibility of changing ship hull geometries in the numerical analysis, the CFD based maneuvering simulations have been playing an important role to study a ship’s maneuverability. Similar as model tests, the CFD-based methods have been utilized to simulate all different maneuvering test scenarios. The most complex one is to employ the high-fidelity CFD analysis to simulate free running tests with steering rudder and rotating propeller in time domain (Dubbioso et al. 2016, Islam and Guedes Soares 2018). These CFD-based methods were used to simulate very complicated navigation scenarios even without too much model test experiences, such as the free running ship motions in following waves (Akari et al. 2019), the hull-propulsor-engine interaction during a ship’s maneuvering (el Moctar et al. 2016), and the turn and zigzag maneuvers for catamarans (Duman and Bal 2022).
However, due to huge cost in terms of either infrastructure or computational resources related to model tests and high fidelity CFD methods, different mathematical maneuvering models and corresponding parameter identification methods have been extensively studied to predict a ship’s maneuverability. The so-called system identification methods for ship maneuvering are based on model tests or CFD simulations as inputs but can help to significantly reduce the number of tests in those methods (Perera et al. 2016, Alexandersson 2024). When model or field tests were used for identification, a large effort should be made to find robust algorithms for data cleaning and data-driven models (Revestido et al. 2012, Alexandersson 2022, Du et al. 2022); while when CFD-based simulations were used as inputs, sensitivities of CFD analysis settings should be investigated since the data from the numerical simulations are ideal (Liu et al. 2018).
For conventional ships, different mathematical models to describe their maneuverability are well investigated, while empirical formulas to some maneuvering components are available (Yasukawa and Yoshimura 2015). For ships with WAPS installed, ship maneuverability can be significantly affected due to extra WAPS and large rudders, which can cause different flow characteristics for propeller-rudder interactions and obvious drifting. Very little experience is available to model their maneuverability. In this study, a systematic approach is proposed to obtain the hydrodynamic coefficients and hydrodynamic derivatives in the MMG model, as well as the modeling of rudder forces in various drifting conditions. Limited amount of tests data and cheap CFD-based virtual captive tests are proposed to obtain some necessary parameters in the MMG model. Two ships designed with WAPS and different propulsion settings are used in this study to validate the proposed approach. For the complete description of the proposed method, the left part of the paper is organized as follows. 


%A ship is a system that transports passengers and goods on water. Manoeuvring, is a fundamental aspect of this system. The ability to control the ship from departure to destination along a desired route, avoiding obstacles such as land and other ships is an essential. The IMO standards for manoeuvrability highlights the importance of the ship manoeuvring. The performance can be assessed by conducting standard manoeuvres with the real built system – the ship, during sea trials. Revealing a substandard manoeuvring performance at this stage is however undesirable, where the possibilities for design changes are very limited and costly. This calls for earlier assessments, before the ship is build, which is traditionally done in scale model tests with a free sailing model.

%With the advancement of numerical methods, CFD is an alternative, which may be more cost efficient and potentially more accurate, where the scale effect problem can be avoided by conducting full scale simulations. Direct CFD calculations in the time domain, visiting all the states during a manoeuvre, are however computationally expensive, even more expensive than the scale model tests and is therefore mostly applied in a research context, than in commercial ship building projects.

%Virtual captive tests (VCT) can be used to reduce the computational effort by only calculating a few potential states of a manoeuvre with CFD. The calculated forces acting on the ship for the sampled states can be used to develop a prediction model, which can be used to simulate the unseen states during the manoeuvre.  

%The CFD calculations for the VCT in this paper are assumed to have sufficient accuracy. The accuracy of the CFD itself will therefore not be questioned. Instead, the accuracy of the hydrodynamic discretization in developing a system based model from a set of VCT is the main focus.  